### 2022-04-21 input/appendices.tex
rework order and appendix

>>>>

\section{Proof of Theorem~\ref{theo:fb}}
\label{appendix:fb}

\begin{proof}
  Whenever a \process~$s$ becomes a source, it broadcasts hence
  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
  its set of received messages, it acknowledges that it belongs to its
  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
  \noindent Such a source forwards its notification to its neighbors.
  Every neighbor eventually receives its notification since
  communication links are reliable. Whatever the order of received
  messages $R_x$ at neighboring \process~$x$, total order ensures that
  it delivers notifications $\alpha_s^{d}$ when
  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
  this case.
  \noindent Among these neighbors, at least those that fulfill the
  latest condition forward their respective notification.  By
  transitivity, the message originating from $s$ reaches all
  \processes that belong to $P_s$ at least through their respective
  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
  quiescent, \ie no \process becomes source anymore, every \process
  eventually acknowledges the partition it belongs to, \ie \processes
  eventually reach consistent partitioning together. In addition, the
  protocol terminates: a \process never delivers hence forwards a
  message after it received, delivered, and forwarded the message of
  its closest source from its lightest path.
\end{proof}

\section{Proof of Theorem~\ref{theo:fbfsdcp}}
\label{appendix:fbfsdcp}

\begin{proof}
  Detection triggers forwarding of staleness downstream which
  completes the case study of Lemma~\ref{lem:detector} by ensuring
  that, when a source broadcasts its staleness notification, all
  \processes that belong to its partition eventually deliver such a
  staleness notification. All downstream bordering \processes also
  eventually receive such a staleness notification and echo back their
  best delivered message. This triggers another competition as in
  Theorem~\ref{theo:fb} for the \processes that delivered the
  staleness notification.
\end{proof}

%% \section{Related work summary}

%% Table~\ref{table:relatedwork} provides a summary of state-of-the-art
%% approaches along with the reason they fail to enable quick content
%% indexing in large scale dynamic systems.

%% \input{input/tablerelatedwork.tex}

### 2022-04-21 input/proposal.tex
rework order and appendix

\begin{proof}
  Whenever a \process~$s$ becomes a source, it broadcasts hence
  delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
  its set of received messages, it acknowledges that it belongs to its
  own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
  it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
  \noindent Such a source forwards its notification to its neighbors.
  Every neighbor eventually receives its notification since
  communication links are reliable. Whatever the order of received
  messages $R_x$ at neighboring \process~$x$, total order ensures that
  it delivers notifications $\alpha_s^{d}$ when
  $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
  is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
  this case.
  \noindent Among these neighbors, at least those that fulfill the
  latest condition forward their respective notification.  By
  transitivity, the message originating from $s$ reaches all
  \processes that belong to $P_s$ at least through their respective
  lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
    |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
    d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
  quiescent, \ie no \process becomes source anymore, every \process
  eventually acknowledges the partition it belongs to, \ie \processes
  eventually reach consistent partitioning together. In addition, the
  protocol terminates: a \process never delivers hence forwards a
  message after it received, delivered, and forwarded the message of
  its closest source from its lightest path.
\end{proof}

@@

\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \implies \textup{DCP}$]
  A protocol guarantees dynamic consistent partitioning if it
  implements forwarding of best up-to-date messages with echos,
  forwarding of staleness messages downstream, and the detection of
  possible blocking triggers the forwarding of staleness notifications
  downstream.
\end{theorem}

\begin{proof}
  Detection triggers forwarding of staleness downstream which
  completes the case study of Lemma~\ref{lem:detector} by ensuring
  that, when a source broadcasts its staleness notification, all
  \processes that belong to its partition eventually deliver such a
  staleness notification. All downstream bordering \processes also
  eventually receive such a staleness notification and echo back their
  best delivered message. This triggers another competition as in
  Theorem~\ref{theo:fb} for the \processes that delivered the
  staleness notification.
\end{proof}

>>>>

\begin{proof}
  Proof in Appendix~\ref{appendix:fb}.
%%   Whenever a \process~$s$ becomes a source, it broadcasts hence
%%   delivers its own message $d_s(\alpha_{s}^{|\pi_{ss}|})$. Whatever
%%   its set of received messages, it acknowledges that it belongs to its
%%   own partition $P_s$ since $\alpha_{s}^{|\pi_{ss}|} = \min D_s$ and
%%   it remains forever since $|\pi_{ss}|$ is its greatest lower bound.
%%   \noindent Such a source forwards its notification to its neighbors.
%%   Every neighbor eventually receives its notification since
%%   communication links are reliable. Whatever the order of received
%%   messages $R_x$ at neighboring \process~$x$, total order ensures that
%%   it delivers notifications $\alpha_s^{d}$ when
%%   $d= |\pi_{ss}| + w_{sx} = \min |\pi_{s'x}|$ where $\min |\pi_{s'x}|$
%%   is the lightest weight of $x$ to any source $s'$, $s'$ being $s$ in
%%   this case.
%%   \noindent Among these neighbors, at least those that fulfill the
%%   latest condition forward their respective notification.  By
%%   transitivity, the message originating from $s$ reaches all
%%   \processes that belong to $P_s$ at least through their respective
%%   lightest path: $\small\smash{\forall y \in V, s, s' \in S: \min
%%     |\pi_{s y}| < \min |\pi_{s' y}| \implies \eventually
%%     d_{y}(\alpha_{s}^{\min |\pi_{sy}|})}$. When the system becomes
%%   quiescent, \ie no \process becomes source anymore, every \process
%%   eventually acknowledges the partition it belongs to, \ie \processes
%%   eventually reach consistent partitioning together. In addition, the
%%   protocol terminates: a \process never delivers hence forwards a
%%   message after it received, delivered, and forwarded the message of
%%   its closest source from its lightest path.
\end{proof}

@@

\begin{theorem}[\label{theo:fbfsdcp}$\textup{FB}^+ \wedge \textup{FS}^+ \implies \textup{DCP}$]
  A protocol guarantees dynamic consistent partitioning if it
  implements forwarding of best up-to-date messages with echos,
  forwarding of staleness messages downstream, and the detection of
  possible blocking triggers the forwarding of staleness notifications
  downstream.
\end{theorem}

\begin{proof}
  Proof in Appendix~\ref{appendix:fbfsdcp}.
%%   Detection triggers forwarding of staleness downstream which
%%   completes the case study of Lemma~\ref{lem:detector} by ensuring
%%   that, when a source broadcasts its staleness notification, all
%%   \processes that belong to its partition eventually deliver such a
%%   staleness notification. All downstream bordering \processes also
%%   eventually receive such a staleness notification and echo back their
%%   best delivered message. This triggers another competition as in
%%   Theorem~\ref{theo:fb} for the \processes that delivered the
%%   staleness notification.
\end{proof}
